Embedding Intuitionistic into Classical Logic

### 2022-10-13 FoSSaCS/fossacs-EIICL.tex
abstract

\begin{document}
	%
	\title{Embedding Intuitionistic into Classical Logic}
	%
	%\titlerunning{Abbreviated paper title}
	% If the paper title is too long for the running head, you can set
	% an abbreviated paper title here
	%
	\author{Alexander Pluska \and Florian Zuleger}
	%
	\authorrunning{A. Pluska and F. Zuleger}
	% First names are abbreviated in the running head.
	% If there are more than two authors, 'et al.' is used.
	%
	\institute{TU Wien, Vienna, Austria}
	%
	\maketitle
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques,godel1933intuitionistischen} establishes an embedding from classical into intuitionistic logic. Curiously the reverse direction has not been covered in literature. Based on the work in~\cite{claessen2015sat} we establish a small model property for intuitionistic propositional logic in order to utilize its Kripke semantics to give a simple embedding into classical propositional logic and quantified boolean formulas. We transfer there methods to the first order case and also give an embedding of intuitionistic first-order logic into classical first-order-logic.
This allows a direct application of state-of-the-art classical first-order provers to the problem of determining intuitionistic validity.

For certain classes of benchmarks our approach can compete with state-of-the-art provers, in particular when the intuitionistic content is low. Crucially, our constructions support the transfer of counter-models to validity, which is important to model checking applications, where the output of counter-examples is an appreciated feature.
\end{abstract}

>>>>

\begin{document}
	%
	\title{Embedding Intuitionistic into Classical Logic}
	%
	%\titlerunning{Abbreviated paper title}
	% If the paper title is too long for the running head, you can set
	% an abbreviated paper title here
	%
	\author{Alexander Pluska \and Florian Zuleger}
	%
	\authorrunning{A. Pluska and F. Zuleger}
	% First names are abbreviated in the running head.
	% If there are more than two authors, 'et al.' is used.
	%
	\institute{TU Wien, Vienna, Austria}
	%
	\maketitle
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques,godel1933intuitionistischen} establishes an embedding from classical into intuitionistic logic.
Curiously, the reverse direction has not been covered in literature.
Utilizing a normal form for intuitionistic logic~\cite{claessen2015sat}, we establish a small model property for intuitionistic propositional logic.
We use this property for a direct encoding of the Kripke semantics into classical propositional logic and quantified boolean formulas.
Next, we transfer the developed techniques to the first order case and provide an embedding of intuitionistic first-order logic into classical first-order-logic.
Our goal here is an encoding that facilitates the use of state-of-the-art provers for classical first-order logic for determining intuitionistic validity.
In an experimental evaluation, we show that our approach can compete with state-of-the-art provers for certain classes of benchmarks, in particular when the intuitionistic content is low.
We further note that our constructions support the transfer of counter-models to validity, which is an desired feature in model checking applications.
\end{abstract}
